Avoiding tipping points in fisheries management: A Bayesian Non-Parametric approach

### 2014-06-03 manuscripts/manuscript.Rmd
edits from Steve
add caching chunk for render mode

@@

```{r libraries, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
library("knitr")
library("nonparametricbayes") 
library("pdgControl")

>>>>

```{r caching, include=FALSE}
library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)

# PDF-based figures
opts_chunk$set(dev='pdf')
```

@@

```{r libraries, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
library("nonparametricbayes") 
library("pdgControl")
